---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# calcsoap

<!-- badges: start -->
<!-- badges: end -->

The goal of calcsoap is to demonstrate exposing a SOAP client using `gsoap` to generate
C++ code and embed it in an R package via `Rcpp`.

The structure of the package and especially the `Makevars` files (one for each Windows and Linux)
are intented to be used as blueprints for future development (i.e. BDTI).

## Installation

You can install the dev version of calcsoap from [Github](https://github.com/zachzIAM/calcsoap) with:

``` r
remotes::github_install("zachzIAM/calcsoap")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
calcsoap::add(5.5, 6.6)
calcsoap::sub(5.5, 6.6)
calcsoap::mul(5.5, 6.6)
calcsoap::div(5.5, 6.6)
calcsoap::pow(5.5, 6.6)
```
